% Bibliography
\clearpage
\begin{thebibliography}{99}

\bibitem{chen2016xgboost}
T. Chen and C. Guestrin, ``XGBoost: A Scalable Tree Boosting System,'' \textit{Proceedings of the 22nd ACM SIGKDD}, pp. 785--794, 2016.

\bibitem{fischer2018lstm}
T. Fischer and C. Krauss, ``Deep learning with long short-term memory networks for financial market predictions,'' \textit{European Journal of Operational Research}, vol. 270, no. 2, pp. 654--669, 2018.

\bibitem{dietterich2000ensemble}
T. G. Dietterich, ``Ensemble Methods in Machine Learning,'' \textit{International Workshop on Multiple Classifier Systems}, Springer, pp. 1--15, 2000.

\bibitem{bailey2014lookahead}
D. H. Bailey, J. Borwein, M. L\'opez de Prado, and Q. J. Zhu, ``Pseudomathematics and Financial Charlatanism: Backtest Overfitting,'' \textit{Notices of the AMS}, vol. 61, no. 5, pp. 458--471, 2014.

\bibitem{prado2018walkforward}
M. L\'opez de Prado, ``Advances in Financial Machine Learning,'' \textit{Wiley Finance}, 2018.

\bibitem{bollen2011twitter}
J. Bollen, H. Mao, and X. Zeng, ``Twitter mood predicts the stock market,'' \textit{Journal of Computational Science}, vol. 2, no. 1, pp. 1--8, 2011.

\bibitem{loughran2011sentiment}
T. Loughran and B. McDonald, ``When is a Liability not a Liability?'' \textit{The Journal of Finance}, vol. 66, no. 1, pp. 35--65, 2011.

\bibitem{moody2001rl}
J. Moody and M. Saffell, ``Learning to Trade via Direct Reinforcement,'' \textit{IEEE Trans. Neural Networks}, vol. 12, no. 4, pp. 875--889, 2001.

\bibitem{deng2016rl}
Y. Deng, F. Bao, Y. Kong, Z. Ren, and Q. Dai, ``Deep Direct Reinforcement Learning for Financial Signal Representation,'' \textit{IEEE Trans. NNLS}, vol. 28, no. 3, pp. 653--664, 2016.

\bibitem{theate2021dqn}
T. Th\'eate and D. Ernst, ``An Application of Deep Reinforcement Learning to Algorithmic Trading,'' \textit{Expert Systems with Applications}, vol. 173, 2021.

\bibitem{zhang2020xgboost}
Y. Zhang, L. Wu, and Q. Chen, ``Stock Price Prediction Using XGBoost and LSTM,'' \textit{Journal of Physics: Conf. Series}, vol. 1584, 2020.

\bibitem{kumar2022indian}
R. Kumar and A. Sharma, ``Ensemble-based stock market prediction for Indian equities,'' \textit{Int. J. Computational Intelligence Systems}, vol. 15, no. 1, pp. 1--15, 2022.

\bibitem{singh2023ml}
P. Singh and V. Gupta, ``Machine Learning for Indian Stock Market: A Comparative Study,'' \textit{J. Financial Data Science}, vol. 5, no. 2, pp. 82--97, 2023.

\bibitem{shah2021ensemble}
D. Shah, H. Isah, and F. Zulkernine, ``Stock Market Analysis: A Review and Taxonomy of Prediction Techniques,'' \textit{Int. J. Financial Studies}, vol. 7, no. 2, pp. 1--32, 2019.

\bibitem{hochreiter1997lstm}
S. Hochreiter and J. Schmidhuber, ``Long Short-Term Memory,'' \textit{Neural Computation}, vol. 9, no. 8, pp. 1735--1780, 1997.

\bibitem{cho2014gru}
K. Cho et al., ``Learning Phrase Representations using RNN Encoder--Decoder,'' \textit{EMNLP}, pp. 1724--1734, 2014.

\bibitem{wolpert1992stacking}
D. H. Wolpert, ``Stacked Generalization,'' \textit{Neural Networks}, vol. 5, no. 2, pp. 241--259, 1992.

\bibitem{sezer2020survey}
O. B. Sezer et al., ``Financial time series forecasting with deep learning: A systematic review,'' \textit{Applied Soft Computing}, vol. 90, 2020.

\bibitem{lim2021tft}
B. Lim et al., ``Temporal Fusion Transformers for Multi-horizon Time Series Forecasting,'' \textit{Int. J. Forecasting}, vol. 37, no. 4, pp. 1748--1764, 2021.

\bibitem{mnih2015dqn}
V. Mnih et al., ``Human-level control through deep reinforcement learning,'' \textit{Nature}, vol. 518, pp. 529--533, 2015.

\bibitem{araci2019finbert}
D. Araci, ``FinBERT: Financial Sentiment Analysis with Pre-trained Language Models,'' \textit{arXiv:1908.10063}, 2019.

\end{thebibliography}


